Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-24 paper.tex
Removed duplicate 'future' in last paragraph

Either way, it is hoped that the lessons learned in this report, namely that
rendering volumes is inherently fragment-bound and avoiding any unnecessary
processing with early ray termination is key to achieving significant speed-ups,
will prove valuable to future future endeavors in both volume rendering and
graphics in general.

>>>>

Either way, it is hoped that the lessons learned in this report, namely that
rendering volumes is inherently fragment-bound and avoiding any unnecessary
processing with early ray termination is key to achieving significant speed-ups,
will prove valuable to future endeavors in both volume rendering and graphics in
general.
